Nitrogen's form determines its fate in the North Pacific Subtropical Gyre

### 2025-05-22 README.Rmd
Fixing image alignment

<div style="display: flex; align-items: center;">
  <img src="manuscript/figures/MAA_curves.png" style="width: 50%; margin-right: 10px;" />
  <div style="text-align: center; flex: 1;">
    <p>Figure 3: Fraction of UV-reactive mycosporine-like amino acids (MAAs) containing at least one ^15^N label over one day during the treatments amended with ^15^N labeled ammonia or nitrate. Incubations started at 6AM are shown in yellow while incubations started at 6PM are shown in blue, with grey background regions highlighting nighttime. Three replicates are included at each of the 5 timepoints and best-fit power law curves have been fit behind the data.</p>
  </div>
</div>

<div clear="left"></div>

>>>>

<table>
  <tr>
    <td>
      <img src="manuscript/figures/MAA_curves.png" width="4500"/>
    </td>
    <td style="vertical-align: middle; text-align: center;">
      Figure 3: Fraction of UV-reactive mycosporine-like amino acids (MAAs) containing at least one ^15^N label over one day during the treatments amended with ^15^N labeled ammonia or nitrate. Incubations started at 6AM are shown in yellow while incubations started at 6PM are shown in blue, with grey background regions highlighting nighttime. Three replicates are included at each of the 5 timepoints and best-fit power law curves have been fit behind the data.
    </td>
  </tr>
</table>
